Flowchart of Current Algorithm

### 2008-10-24 docs/flowchart/flowchart.tex
add plane-parallel description of Advect Base Density, Pressure, and Enthalpy

\item {\bf Advect Base}$[\rho_0^{\inp}, (\rho h)_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp}] \rightarrow [\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp}]$ \\
is the process by which we update the base state through $\dt$ in
time \MarginPar{we need a separate section for spherical} given the
radial velocity $w_0^{\inp}.$ The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.

\begin{enumerate}
\renewcommand{\labelenumii}{{\bf \alph{enumii}}.}

\item For the density update, we discretize equation the base state
  density evolution equation (paper III; eq.~[29]) without the $\etarho$ term,
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
\enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
to compute the new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ]
         \nonumber \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.

\item For the pressure update, we discretize the base state pressure
  evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp 
\enskip,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in the forcing for
the interface state calculation, but is used in the update.

\item For the enthalpy update, we discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] + \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left\{ \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j+\myhalf} -  
         \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j-\myhalf} \right\}
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.

@@

\MarginPar{we need to write the spherical description}

>>>>

\item {\bf Advect Base Density}$[\rho_0^\inp,w_0^\inp]$
$\rightarrow [\rho_0^\outp,\rho_0^{\outp,n+\myhalf}]$\\
is the process by which we update the base state density through $\dt$ in time
as well as compute time-centered interface states for use later in the algorithm.
\begin{description}

\item[plane-parallel:] We discretize equation the base state density evolution 
equation (paper III; eq.~[29]) without the $\etarho$ term,
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
\enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
to compute the new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ]
         \nonumber \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A.

@@

\item {\bf Advect Base Pressure}$[p_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [p_0^\outp]$\\
is the process by which we update the base state pressure through $\dt$ in time.
\begin{description}

\item[plane-parallel:] We discretize the base state pressure
  evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp 
\enskip,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in the forcing for
the interface state calculation, but is used in the update.

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [(\rho h)_0]^\outp$\\
is the process by which we update the base state enthalpy through $\dt$ in time.
\begin{description}

\item[plane-parallel:] We discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] 
+ \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left\{ \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j+\myhalf} -  
         \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j-\myhalf} \right\}
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.
